Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-11 WSSSPE1_report/WSSSPE1_summary_report.tex
Adding Elster paper summary.

>>>>

While many papers briefly discussed licensing issues, \cite{Elster_WSSSPE}
directly discussed the impact of different licenses on obtaining industrial
funding for scientific software projects.  In particular, the author describes
experiences with researchers unwilling to utilize GPL (copyleft) code, as it
adds restrictions to reuse that some industries find unacceptable for future
commercialization.  (This was discussed in \cite{Hanwell_WSSSPE} as well.)
Further obstacles to sustainability identified by the author include patenting
of software, a lack of open access, and even more broadly, a lack of open
source codes even in open access journals.  Finally, a lack of awareness on the
part of scientific software developers of commodity libraries for common tasks
reduces their ability to reuse code.
